Astr 513: Final Project

### 2016-05-05 Final_Project/ms.tex
Redcued the width of the correlation matrix figures so that they don't each take up a page.
Improved figure captions.

The correlation matrix is calculated from the covariance matrix according to
%
\begin{equation}
  \label{eq:correlation}
  Corr_{i,j} = \frac{\mathbf{C}_{i,j}}{\sqrt{\mathbf{C}_{i,i}}\sqrt{\mathbf{C}_{j,j}}}.
\end{equation}
%
Note that the correlation of a variable with itself is 1 by definition.
The correlation matrices for both of our data sets can be seen below in
figures \autoref{fig:cmatrix_betoule} and \autoref{fig:cmatrix_rest}.

\TM{TODO: Discuss how the correlation matrices for the two data sets are different
  and hypothesize on what this might mean.}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/Betoule_correlation.eps}
 \caption{Correlation matrix of $\mu_0(z)$ from the
 \citet{betoule2014} sample.
 \TM{Need to improve this caption.}}
 \label{fig:cmatrix_betoule}
\end{figure}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/Rest_correlation.eps}
 \caption{Correlation matrix of $\mu_0(z)$ from the
 \citet{rest2014} sample.
 \TM{Need to improve this caption.}}
 \label{fig:cmatrix_rest}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=\linewidth]{figures/corner_example.eps}
 \caption{Example corner plot.}
 \label{fig:corner}
\end{figure}

>>>>

The correlation matrix is calculated from the covariance matrix according to
%
\begin{equation}
  \label{eq:correlation}
  Corr_{i,j} = \frac{\mathbf{C}_{i,j}}{\sqrt{\mathbf{C}_{i,i}}\sqrt{\mathbf{C}_{j,j}}}.
\end{equation}
%
Note that the correlation of a variable with itself is 1 by definition.
The correlation matrices for both of our data sets can be seen below in
figures \autoref{fig:cmatrix_betoule} and \autoref{fig:cmatrix_rest}.
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Betoule_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{betoule2014} sample. Overall very few correlations exist between
    samples, likely due to the averaging over redshift bins.}
  \label{fig:cmatrix_betoule}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Rest_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{rest2014} sample. Significant correlation exist between
    different samples due to dependencies on systematic variables
    as seen in \autoref{eq:RestCovMatrix}.}
  \label{fig:cmatrix_rest}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/corner_example.eps}
  \caption{Example corner plot.}
  \label{fig:corner}
\end{figure}
